Tree regeneration in models of forest dynamics: a key priority for further research

### 2023-05-15 manuscript/manuscriptRW.Rmd
data statement added

---
pretitle: "Journal: Ecological Monographs. Manuscript type: Article"
title: "Tree regeneration in models of forest dynamics: a key priority for further research"
author: 
- Olalla Díaz-Yáñez$^{*1}$, 
- Yannek Käber$^1$, 
- Tim Anders$^2$,
- Friedrich Bohn$^3$,
- Kristin H. Braziunas$^4$,
- Josef	Brůna$^5$,
- Rico Fischer$^3$,
- Samuel M. Fischer$^3$,
- Jessica Hetzer$^2$,
- Thomas Hickler$^2$,
- Christian	Hochauer$^6$,
- Manfred J. Lexer$^6$,
- Heike	Lischke$^7$,
- Mats Mahnken$^8$,
- Paola	Mairota$^9$,
- Ján Merganič$^{10}$,
- Katarina Merganičová$^{11,12}$,
- Tobias Mette$^{13}$,
- Marco Mina$^{14}$,
- Xavier Morin$^{15}$
- Werner Rammer$^4$,
- Christopher P.O. Reyer$^8$,
- Simon	Scheiter$^2$,
- Daniel Scherrer$^{16}$,
- Harald Bugmann$^1$
date: $^*$Corresponding author (olalla.diaz@usys.ethz.ch) \newline
      $^1$ETH Zurich. Department of Environmental Systems Science. Institute of Terrestrial Ecosystems. Universitätstrasse 16, 8092 Zürich, Switzerland. \newline
      $^2$Senckenberg Biodiversity and Climate Research Centre (SBiK-F), 60325 Frankfurt am Main, Germany. \newline
      $^3$Department of Computational Hydrosystem, Helmholtz-Centre for Environmental Research - UFZ, Permoserstraße 15, 04318 Leipzig, Germany. \newline
      $^4$Ecosystem Dynamics and Forest Management Group, TUM School of Life Sciences, Technical University of Munich, 85354 Freising, Germany. \newline
       $^5$Department of Geoecology, Institute of Botany of the Czech Academy of Sciences, Průhonice, Czech Republic. \newline
       $^6$Institute of Silviculture, Department of Forest and Soil Sciences, University of Natural Resources and Life Sciences, Peter Jordan Strasse 82, A-1190 Vienna, Austria \newline
       $^7$Dynamic Macroecology, Swiss Federal Institute for Forest, Snow and Landscape Research WSL, Zürcherstrasse 111, 8903 Birmensdorf, Switzerland. \newline
       $^8$Potsdam Institute for Climate Impact Research (PIK), Member of the Leibniz Association, 14473 Potsdam, Germany. \newline
       $^9$Department of Soil Sciences, of Plants and Food, University of Bari Aldo Moro, Italy. \newline
       $^{10}$Department of Forest Harvesting, Logistics and Ameliorations, Faculty of Forestry, Technical University in Zvolen \newline
       $^{11}$Czech University of Life Sciences Prague, Faculty of Forestry and Wood Sciences, Kamýcká 129, 16500 Praha 6 – Suchdol, Czech Republic. \newline
       $^{12}$Department of Biodiversity of Ecosystems and Landscape, Slovak Academy of Sciences, Štefánikova 3, P.O.Box 25, 81499 Bratislava, Slovakia. \newline 
       $^{13}$Dpt. of Soil and Climate, Bavarian State Institute of Forestry. \newline 
       $^{14}$Institute for Alpine Environment, Eurac Research, Bolzano/Bozen, Italy. \newline 
       $^{15}$CEFE, CNRS Campus du CNRS 1919, route de Mende 34293 Montpellier cedex, France. \newline 
       $^{16}$Swiss Federal Institute for Forest, Snow and Landscape Research WSL, Zürcherstrasse 111, 8903 Birmensdorf, Switzerland
    \newline  
    \newline
    \today 
output:
  bookdown::pdf_document2:
    keep_tex: yes
    number_sections: yes
    toc: no
    extra_dependencies: "subfig"
  word_document:
    reference_docx: template_paper.docx
mainfont: Arial
fontsize: 12pt
linestretch: 1.5
bibliography: Regeneration.bib
link-citations: yes
nocite: |
  @bugmann1996a, @bohn2014, @fabrika2005, @mette2014, @smith2001a, @langan2017, @seidl2012a, @lischke2006, @schumacher2006, @scheiter2009, @scheller2007, @morin2021, @lasch-born2020, @hickler2012, @fischer_lessons_2016, @langan2017, @scheiter2013 
linkcolor: blue
csl: global-change-biology.csl
editor_options:
  markdown:
    wrap: 72
header-includes:
- \usepackage[left]{lineno}
- \linenumbers
- \usepackage{caption}
- \captionsetup[figure]{font=scriptsize}
- \captionsetup[table]{font=scriptsize}
- \usepackage{titling}
- \predate{\begin{flushleft}}
- \postdate{\end{flushleft}}
---

@@

@@

# Reproducibility and data availability statement

This study complies with the basic rules of reproducibility and has made available the protocol of the study, the data and all the software that has led to the findings presented in this paper. The protocol is available at @díaz-yáñez2022. The code and data that support the findings of this study are openly available at zenodo (*link to be added*) and github (*link to be added*) [for the review process we have provided these materials [on this link](https://polybox.ethz.ch/index.php/s/q5MOB1CLcjARs3H) (password: DownDataCodeRegen1)].

@@

>>>>

---
title: "Tree regeneration in models of forest dynamics: a key priority for further research"
subtitle: "Submitted to the journal Ecological Monographs. Manuscript type: Article"
author: 
- Olalla Díaz-Yáñez$^{*1}$, 
- Yannek Käber$^1$, 
- Tim Anders$^2$,
- Friedrich Bohn$^3$,
- Kristin H. Braziunas$^4$,
- Josef	Brůna$^5$,
- Rico Fischer$^3$,
- Samuel M. Fischer$^3$,
- Jessica Hetzer$^2$,
- Thomas Hickler$^2$,
- Christian	Hochauer$^6$,
- Manfred J. Lexer$^6$,
- Heike	Lischke$^7$,
- Mats Mahnken$^8$,
- Paola	Mairota$^9$,
- Ján Merganič$^{10}$,
- Katarina Merganičová$^{11,12}$,
- Tobias Mette$^{13}$,
- Marco Mina$^{14}$,
- Xavier Morin$^{15}$
- Werner Rammer$^4$,
- Christopher P.O. Reyer$^8$,
- Simon	Scheiter$^2$,
- Daniel Scherrer$^{16}$,
- Harald Bugmann$^1$
date: $^1$ETH Zurich. Department of Environmental Systems Science. Institute of Terrestrial Ecosystems. Universitätstrasse 16, 8092 Zürich, Switzerland. \newline
      $^2$Senckenberg Biodiversity and Climate Research Centre (SBiK-F), 60325 Frankfurt am Main, Germany. \newline
      $^3$Department of Computational Hydrosystem, Helmholtz-Centre for Environmental Research - UFZ, Permoserstraße 15, 04318 Leipzig, Germany. \newline
      $^4$Ecosystem Dynamics and Forest Management Group, TUM School of Life Sciences, Technical University of Munich, 85354 Freising, Germany. \newline
       $^5$Department of Geoecology, Institute of Botany of the Czech Academy of Sciences, Průhonice, Czech Republic. \newline
       $^6$Institute of Silviculture, Department of Forest and Soil Sciences, University of Natural Resources and Life Sciences, Peter Jordan Strasse 82, A-1190 Vienna, Austria \newline
       $^7$Dynamic Macroecology, Swiss Federal Institute for Forest, Snow and Landscape Research WSL, Zürcherstrasse 111, 8903 Birmensdorf, Switzerland. \newline
       $^8$Potsdam Institute for Climate Impact Research (PIK), Member of the Leibniz Association, 14473 Potsdam, Germany. \newline
       $^9$Department of Soil Sciences, of Plants and Food, University of Bari Aldo Moro, Italy. \newline
       $^{10}$Department of Forest Harvesting, Logistics and Ameliorations, Faculty of Forestry, Technical University in Zvolen \newline
       $^{11}$Czech University of Life Sciences Prague, Faculty of Forestry and Wood Sciences, Kamýcká 129, 16500 Praha 6 – Suchdol, Czech Republic. \newline
       $^{12}$Department of Biodiversity of Ecosystems and Landscape, Slovak Academy of Sciences, Štefánikova 3, P.O.Box 25, 81499 Bratislava, Slovakia. \newline 
       $^{13}$Dpt. of Soil and Climate, Bavarian State Institute of Forestry. \newline 
       $^{14}$Institute for Alpine Environment, Eurac Research, Bolzano/Bozen, Italy. \newline 
       $^{15}$CEFE, CNRS Campus du CNRS 1919, route de Mende 34293 Montpellier cedex, France. \newline 
       $^{16}$Swiss Federal Institute for Forest, Snow and Landscape Research WSL, Zürcherstrasse 111, 8903 Birmensdorf, Switzerland.  \newline
       $^*$Corresponding author (olalla.diaz@usys.ethz.ch)
output:
  bookdown::pdf_document2:
    keep_tex: yes
    number_sections: yes
    toc: no
    extra_dependencies: "subfig"
  word_document:
    reference_docx: template_paper.docx
mainfont: Arial
fontsize: 12pt
linestretch: 1.5
bibliography: Regeneration.bib
link-citations: yes
nocite: |
  @bugmann1996a, @bohn2014, @fabrika2005, @mette2014, @smith2001a, @langan2017, @seidl2012a, @lischke2006, @schumacher2006, @scheiter2009, @scheller2007, @morin2021, @lasch-born2020, @hickler2012, @fischer_lessons_2016, @langan2017, @scheiter2013 
linkcolor: blue
csl: global-change-biology.csl
editor_options:
  markdown:
    wrap: 72
header-includes:
- \usepackage[left]{lineno}
- \linenumbers
- \usepackage{caption}
- \captionsetup[figure]{font=scriptsize}
- \captionsetup[table]{font=scriptsize}
- \usepackage{titling}
- \predate{\begin{flushleft}}
- \postdate{\end{flushleft}}
---

@@

OPEN RESEARCH STATEMENT: This submission uses novel code, both the data and code are provided in an external repository to be evaluated during the peer review process. The repository can be downloaded from [here](https://polybox.ethz.ch/index.php/s/q5MOB1CLcjARs3H) (password: DownDataCodeRegen1)]. The protocol is available at @díaz-yáñez2022. We will make publicly available the code and data after the revision.

**Keywords:** tree regeneration | tree recruitment | tree establishment | forest dynamics | models | landscape | stand | global

@@

# Author contributions
O. Díaz-Yáñez and Y. Käber contributed equally and share the first authorship. H. Bugmann, Y. Käber, and O. Díaz-Yáñez developed the study design. All authors contributed to preparing the simulations with their respective models. O. Díaz-Yáñez led the data analysis with contributions during the workshop from Y.Käber, T. Anders, K. H. Braziunas, J. Brůna, S. M. Fischer, J. Hetzer, T. Hickler, H. Lischke, M.Mahnken, P. Mairota, K. Merganičová, T. Mette, X. Morin, W. Rammer and D. Scherrer
H. Bugmann. O. Díaz-Yáñez and H. Bugmann led the writing of the manuscript. All authors participated in the revision of the manuscript and approved its submission.

@@

# Conflict of interest statement

The authors declare no conflicts of interest.
